---
output: github_document
---

# r-dcm hex stickers

```{r, echo = FALSE, message = FALSE}
library(magick)
logos <- tools::file_path_sans_ext(dir("png-hires", pattern = "\\.png$"))
png <- paste0("png-hires/", logos, ".png")
svg <- paste0("svg/", logos, ".svg")
thumb <- paste0("thumbs/", logos, ".png")

resize <- function(path_in, path_out) {
  image <- image_read(path_in)
  image <- image_resize(image, "278x")
  image_write(image, path_out)
}

outdated <- !file.exists(thumb) | file.mtime(thumb) < file.mtime(png)
invisible(Map(resize, png[outdated], thumb[outdated]))
```

```{r, results = "asis", echo = FALSE}
img <- glue::glue('<img alt="Logo for {logos}" src="{thumb}" width="120" height="139">')
png_link <- glue::glue('<a href="{png}">{logos}.png</a>')
svg_link <- glue::glue('<a href="{svg}">{logos}.svg</a>')
cell <- paste0("<td>", img, "<br />", png_link, "<br />", svg_link, "</td>")

cols <- 5
rows <- ceiling(length(cell) / cols)

row_id <- rep(seq_len(rows), each = cols, length.out = length(cell))
row_cells <- split(cell, row_id)

cat("<table>\n")
cat(paste0("<tr>", sapply(row_cells, paste, collapse = ""), "</tr>"), sep = "")
cat("</table>\n")
```

All stickers are licensed [CC0](LICENSE.md). 

## Printing

Look for a company that offers die-cut stickers. We recommend using the PNG version of the sticker. The printed stickers should be 1.74" x 2". 

If you use the SVG version:

* Specify colors as CMYK using the U.S. Web Coated (SWOP) v2 profile.
* Save a copy of your final sticker and convert all text to outlines to avoid font problems.
